---
title: "Vignettes"
author: "Daniel Seo"
date: "5/1/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
```

```{r setup, include=FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
library(ggplot2)
```

## bin_choose(n, k)

For us to calculate the probability of binomial distribution with given number of trials, probability, and success, we first have to calculate the number of combinations in which k success can occur in n trials.

```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:4)
```

## bin_probability(success, trials, prob)

We then are able to calculate the probability with given values of success, trials, and prob.
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:3, trials = 5, prob = 0.5)
bin_probability(success = 45, trials = 100, prob = 0.55)
```

## bin_distribution(trials, prob)

We now can get data frame with the binomial probability distribution.

```{r}
bin_distribution(5, 0.5)
```

We use barplot() to display the probability histogram of the binomial distribution.

```{r}
dist <- bin_distribution(5, 0.5)
plot(dist)
```

## bin_cumulative()

Now let's get the data frame with both the probability distribution and the cummulative probabilities.
```{r}
bin_cumulative(5, 0.5)
```

Use barplot() to display the cumulative distribution.
```{r}
dist2 <- bin_cumulative(5, 0.5)
plot(dist2)
```

## bin_variable()

This function calculates cumulative binomial distribution given the number of trials and probability.
```{r}
bin_variable(10, 0.2)
```

The `summary()` function returns a table of relavant statistics of binomial distribution.
```{r}
bins <- bin_variable(10, 0.3)
binsums<- summary(bins)
binsums
```
